### 2018-05-09 Paper/method.tex
..

\noindent where $N_l$ is the number of training points, 
$\widetilde{\mu}~=~\frac{1}{N}\sum\limits_{i=1}^N G(\bm{\theta}_i)$
is the sample mean of the model response, and $ G^{\mbox{\tiny {PC}\textbackslash i}}$
is the PCE surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
From Eq.~\ref{eq:loo}, it appears that $N$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
independent of $\mathcal{Y}^{\mbox{\tiny {PC}\textbackslash i}}$ is used.

>>>>

\noindent where $N_l$ is the number of training points, 
$\widetilde{\mu}~=~\frac{1}{N}\sum\limits_{i=1}^N G(\bm{\theta}_i)$
is the sample mean of the model response, and $ G^{\mbox{\tiny {PC}\textbackslash i}}$
is the PCE surrogate constructed using all but the $i^{\mbox{\tiny{th}}}$ model realization. 
From Eq.~\ref{eq:loo}, it appears that $N$ PCEs are needed to evaluate $\epsilon_{\mbox{\tiny LOO}}$.
However, in practice a modified formulation for $\epsilon_{\mbox{\tiny LOO}}$~\cite{Blatman:2009},
independent of $G^{\mbox{\tiny {PC}\textbackslash i}}$ is used.
